Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-04-05 faces_system.tex
Added john's bio

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/arvind}}]{John Wright}
Arvind Ganesh received his Bachelor's and Master's degrees, both in Electrical
Engineering, from the Indian Institute of Technology, Madras, India in 2006. He
is currently a PhD candidate in the Electrical \& Computer Engineering
Department at the University of Illinois, Urbana-Champaign. His research
interests include compressed sensing, computer vision, and machine learning.
His recent work focuses on low-rank matrix recovery techniques for
batch image alignment and texture rectification.  \end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{bios/john}}]{John Wright}
John Wright received his PhD in Electrical Engineering from the University of Illinois at Urbana-Champaign in October 2009. He is currently a researcher in the Visual Computing group at Microsoft Research Asia. His research focuses on developing provably correct and efficient tools for recovering low-dimensional structure in high-dimensional datasets, even when data are missing or grossly corrupted. These techniques address critical estimation problems in imaging and vision applications such as automatic face recognition, video stabilization and tracking, image and data segmentation, and more. They also find application outside of vision, for example in web data analysis and bioinformatics. His work has received a number of awards and honors, including the 2009 Lemelson-Illinois Prize for Innovation for his work on robust face recognition, the 2009 UIUC Martin Award for Excellence in Graduate Research, a 2008-2010 Microsoft Research Fellowship, a Carver fellowship, and a UIUC Bronze Tablet award.
\end{IEEEbiography}
